On Secure Delegation of SampBQP with a Classical Client

### 2019-11-24 hamiltonian.tex
Type out QPIP protocol

\begin{observation}
	Given XZ-circuit $C$ and $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtain $C'$. One can then measure the last register of $\psi_{C'(x)}$ and obtain with probabiliy $\frac{1}{2}$ the state $C(x)$.
\end{observation}

>>>>

\begin{observation}
	\label{idpadding}
	Given XZ-circuit $C$ and $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtain $C'$. One can then measure the last register of $\psi_{C'(x)}$ and obtain with probabiliy $\frac{1}{2}$ the state $C(x)$.
\end{observation}

### 2019-11-24 qpip.tex
Add QPIP XZ estimation for ground state
Fill in simple TODOs
Type out QPIP protocol

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_{XZ}$, or has a $\QPIP_{XZ}$ protocol,  with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is a $\BQP$ machine.
		\item $\bbV$ is a hybrid quantum-classical machine. Its classical part is a $BPP$ machine. Its quantum part is a single-qubit register, on which the verifier can apply only $X$ or $Z$ measurements.
		\item There is a quantum channel between $\bbP$ and $\bbV$ that can transmit one qubit at a time.
		\item There is a classical communication channel between $\bbP$ and $\bbV$.
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

@@

\begin{theorem}
	$\SampBQP$ is in $\QPIP_{XZ}$.
\end{theorem}

@@

TODO Do something about this
\begin{algorithm}
	\floatname{algorithm}{Protocol}
	\caption{Amplification with simple input}
	\label{AlgAmp1}
	\begin{algorithmic}[1]
		\State The prover sends $\poly(n)$ copies of...
		\State The verifier picks $m+n$ copies...
		\State The verifier runs Chernoff bound on...
		\If{number of accepted copies $\geq (\frac{1}{2}-\frac{\varepsilon}{2})n$}
			\State Measure time step...
			\State Output the...
		\Else
			\State Reject
		\EndIf
	\end{algorithmic}
\end{algorithm}
TODO what's $n$?

TODO Talk about de Finetti's here.

Now we consider the general case. We use \autoref{deFinetti}. Let $n=l$ and $k=\poly(n)$, so $\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$ can be arbitrarily inverse-poly small. That is, with some small error in measurement results, we can assume without the loss of generality that the rest of the algorithm acts on an input of the form... TODO.

\begin{theorem}
	When \autoref{AlgAmp1} accepts an input with probability greater than $\delta$, conditioned on this acceptance, $\mathcal{F}$ has probability at least $1-\frac{p}{\delta}$ to accept each register of the output.
\end{theorem}
\begin{proof}
	Note that the input is a classical probability distribution over inputs $\ket{\rho_i^{\otimes n+m}}$ with $w_i$ as weights.

@@

	$\Rightarrow\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}<\frac{p}{\delta}$.
\end{proof}

@@

\Ethan{The above is incredibly handwavy.}

>>>>

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_{XZ}$, or has a $\QPIP_{XZ}$ protocol,  with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is a $\BQP$ machine.
		\item $\bbV$ is a hybrid quantum-classical machine. Its classical part is a $\BPP$ machine. Its quantum part is a single-qubit register, on which the verifier can apply only $X$ or $Z$ measurements.
		\item There is a quantum channel between $\bbP$ and $\bbV$ that can transmit one qubit at a time.
		\item There is a classical communication channel between $\bbP$ and $\bbV$.
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

@@

\begin{theorem}
	There is a $\QPIP_{XZ}$ protocol for \autoref{AlgGroundStateCheck}
\end{theorem}
\begin{proof}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is obvious that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{proof}

\begin{theorem}
	$\SampBQP$ is in $\QPIP_{XZ}$.
\end{theorem}
\begin{proof}

@@

\floatname{algorithm}{Protocol}
\begin{algorithm}
	\caption{Our $\QPIP_{XZ}$ protocol}
	\label{AlgAmp1}
	\begin{algorithmic}[1]
		\State Pick $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\State Pick $n$ large enough so, $P\left[Bin(n, \frac{1}{2}-\varepsilon)<\left(\frac{1}{2}-2\varepsilon\right)n\right]$ is negligible in $\varepsilon$ by Chernoff bound
		\State Pick $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}=O(\poly(\varepsilon))$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
		\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
		\State The verifier randomly picks $n+m$ copies in sequence and without replacement
		\State The verifier runs \autoref{AlgGroundStateCheck} on $n$ of the copies
		\If{over $(\frac{1}{2}-\varepsilon)n$ copies accept}
			\For{$i\gets 1, m$}
				\State Measure the time register of a (supposedly) fresh copy of $\ket{\psi_{C(x)}}$ that the prover sent
				\If{Measured $t\geq T$}
					\State Measure and output the other registers
				\EndIf
			\EndFor
			\State Reject
		\Else
			\State Reject
		\EndIf
	\end{algorithmic}
\end{algorithm}

We first apply \autoref{deFinetti}. This is justified because... TODO

So, with some error $O(\poly(\varepsilon))$ in measurement results, we can assume without the loss of generality that the rest of the algorithm acts on an input of the form... TODO.

Note that the input is a classical probability distribution over inputs $\ket{\rho_i^{\otimes n+m}}$ with $w_i$ as weights.

@@

$\Rightarrow\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}<\frac{p}{\delta}$.

@@

\end{proof}
